Merra2

### 2020-07-16 Rcode/Merra2.Rmd
got it

fileNames<-list.files("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT")

@@

#fix
x198001<-paste0("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT/",x198001) #need full filepath - can you add in loop above??
x200410<-paste0("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT/",x200410)

@@

#the "level" dimension refers to veritcal layers where 72=surface and 1=top of atmosphere
#for a single day

for (i in 1:length (list_all)) {
    for (j in 1:length (list_all[i])){
 bcphilic<-mean(brick(list_all[[i]][[j]], varname="BCPHILIC", level=72)) #one day - first bracket is month, 2nd is day, within a day is 8 layers by hour
bcphobic<-mean(brick(list_all[[i]][[j]], varname="BCPHOBIC", level=72))
ocphilic<-mean(brick(list_all[[i]][[j]], varname="OCPHILIC", level=72))
ocphobic<-mean(brick(list_all[[i]][[j]], varname="OCPHOBIC", level=72))

@@

#Make list of all objects - assign(paste0(“day”,j), <- exact_extract(all, poly, 'mean') -

mean<-exact_extract(raster, poly, 'mean') #extracts mean for each park. Uses cells that intersect polygons.

@@

#take mean of the assign list above
#write csv
  n<-substr(list_all[[1]][[1]],94,100)
    name<-paste0("/Users/killion/",n)
    newname<-paste0(name, ".csv")
write.csv(mean, newname, row.names = FALSE) #save as csv

@@

>>>>

fileNames<-list.files("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT",full.names = TRUE)

@@

#fix - may not have to do this now
# x198001<-paste0("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT/",x198001) #need full filepath - can you add in loop above??
# x200410<-paste0("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT/",x200410)

@@

#the "level" dimension refers to veritcal layers where 72=surface and 1=top of atmosphere
#for a single day
empty_list<-list()

for (i in 1:length (list_all)) {
    for (j in 1:length (list_all[[i]])){
 bcphilic<-mean(brick(list_all[[i]][[j]], varname="BCPHILIC", level=72)) #one day - first bracket is month, 2nd is day, within a day is 8 layers by hour
bcphobic<-mean(brick(list_all[[i]][[j]], varname="BCPHOBIC", level=72))
ocphilic<-mean(brick(list_all[[i]][[j]], varname="OCPHILIC", level=72))
ocphobic<-mean(brick(list_all[[i]][[j]], varname="OCPHOBIC", level=72))

@@

#Make list of all objects - assign(paste0(“day”,j), <- exact_extract(all, poly, 'mean') - 
empty_list[[j]]<-exact_extract(all, poly, 'mean') #intersects boundary

    }
  #take mean of the assign list above

out<-as.data.frame(empty_list)
out_mean<-as.data.frame(rowMeans(out))

#write csv
  n<-substr(list_all[[i]][[j]],94,100) # !!!!!!!! you will have to change this based on the length of your filepaths
  colnames(out_mean)[1] <- n #give values column name based on month
   name<-paste0("/Users/killion/output_means/",n) #create empty folder to save to
    newname<-paste0(name, ".csv")
write.csv(out_mean, newname, row.names = FALSE) #save as csv

@@

#loads those .csv and makes into single df
list_dates = list.files(path="/Users/killion/output_means/", pattern="*.csv", full.names=TRUE) #same folder you saved above output

@@

#save
write.csv(final_means, "/Users/killion/final_means.csv", row.names = FALSE)
